Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft] Proofread intro, add MoM citation

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Introduction
}

@@

The angular distribution of $B\to K \bar\ell\ell$---normalized to the
width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
$\ell^-$ as measured in the dilepton rest frame is
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,.
\end{align}
LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the
angular distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
\mu$~\cite{Aaij:2014tfa}, with unprecedented precision to provide the
lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term
$F_H^\mu$ in CP-averaged form and integrated over several bins in the
dilepton invariant mass $q^2$\fred{sent. too long}. Similarly, the
CP-averaged branching ratios, ${\cal B}_\mu = \tau_{B}
\Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
  CP}^\mu$ \cite{Aaij:2014bsa} are also available from 3 fb$^{-1}$.

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong
suppression factors for vector and dipole couplings present in the SM,
thereby enhancing their sensitivity to tensor and scalar couplings
\cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of scalar
couplings compared to helicity-suppressed vector couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. \fred{Which model gives rise
  to tensor contributions?} Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still
does not allow to perform current angular analysis without the
assumption of vanishing scalar and tensor couplings in this decay
mode. In the future also certain angular observables in $B\to K^*
\bar\ell\ell$ will provide additional constraints on such couplings,
as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the linear
combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the
experimental test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 =
0$~\cite{Bobeth:2012vn}.

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensor and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensor and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensor and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details of the angular observables in $B\to K^* \bar\ell\ell$, the
branching fraction of $B_s\to \bar\mu\mu$ and the
treatment of theory uncertainties are relegated to appendices.

@@

Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again
substantial deviations from the SM prediction are possible only in the
presence of non-zero tensor couplings. In this case enhancement by two
orders of magnitude are possible up to the ${\cal O}(10^{-8})$ at
high-$q^2$ and also at low-$q^2$ in the case of $(J_{1s} - 3\,
J_{2s})$, always being consistent with all included experimental
constraints in \reftab{tab:observables}. In view of current
experimental precision of $20\%$ of the branching ratio measurements
at LHCb \cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to
the ${\cal O}(10^{-8})$, one can indeed hope for some sensitivity to
such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$
for the not yet published 3 fb$^{-1}$ data set.  \todo{Would be a nice
  place to cite method of moments paper?}

>>>>

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
 \checked{ Introduction}
}

@@

The angular distribution of $B\to K \bar\ell\ell$---normalized to the
width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
$\ell^-$ as measured in the dilepton rest frame is
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,.
\end{align}
LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the angular
distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
\mu$~\cite{Aaij:2014tfa}, with unprecedented precision to provide the
lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term $F_H^\mu$
in CP-averaged form and integrated over several bins in the dilepton invariant
mass $q^2$. Similarly, the CP-averaged branching ratios, ${\cal B}_\mu =
\tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
  CP}^\mu$ \cite{Aaij:2014bsa} are also available from 3 fb$^{-1}$.

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole couplings present in the SM, thereby enhancing
their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
helicity-suppressed vector couplings of the SM is well-known from $B_s\to
\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} did not allow to perform a full
angular analysis without the assumption of vanishing scalar and tensor couplings
in this decay mode. In the future with more data or special-purpose analysis
techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
hadronic recoil.

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to
\bar\mu\mu$ to derive stronger constraints than before on tensor and scalar
couplings in various model-independent scenarios and study their impact on the
not yet measured sensitive observables in $B\to K^* \bar\ell\ell$. In
\refsec{sec:EFT}, we specify the effective theory of $|\Delta B| = 1$ decays on
which our model-independent fits are based. Within this theory, we discuss the
dependence of observables in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$
on the tensor and scalar couplings in \refsec{sec:observables} and specify also
the experimental input used in the fits. The constraints on tensor and scalar
couplings from the data are presented for several model-independent scenarios in
\refsec{sec:results}.  Technical details of the angular observables in $B\to K^*
\bar\ell\ell$, the branching fraction of $B_s\to \bar\mu\mu$, the treatment of
theory uncertainties, and the Monte Carlo methods used are relegated to
appendices.

@@

Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
deviations from the SM prediction are possible only in the presence of non-zero
tensor couplings. In this case enhancement by two orders of magnitude are
possible up to the ${\cal O}(10^{-8})$ at high-$q^2$ and also at low-$q^2$ in
the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
experimental constraints in \reftab{tab:observables}. In view of current
experimental precision of $20\%$ of the branching ratio measurements at LHCb
\cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to the ${\cal
  O}(10^{-8})$, one can indeed hope for some sensitivity to such large effects
in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ for the not yet published 3
fb$^{-1}$ data set at least with the method of moments~\cite{beaujean:2015mom}.
